Handling missing data in smartphone location logs

### 2017-11-16 thesisReport.Rmd
updated missingness plot to 5 minute intervals
added two new plots plus an unfinished plot

```{r, accuracyPlot,echo = FALSE,fig.cap="Measurement accuracy of each logged measurement. The x-axis denotes the accuracy in meters such that the user's actual location is expected to be within that radius with 67 percent confidence. Measures were classified into high accuracy (under 800m), medium accuracy (under 5000m) and low accuracy (over 5000m). Measures with accuracy of over 20000m were omitted from the graph. The maximum accuracy measure was over 40000m. Low accuracy measures are often near in time to more high accuracy measures.",out.width = '100%'}

include_graphics("img/accuracyPeter.png")

@@

```{r, measurementsPerDay,echo = FALSE,fig.cap="Missing data over time for the author. The x-axis denotes time, the y-axis shows how many measurements are made and each point is a day. The fill of the points shows the amount of hours of captured data each day.",out.width = '100%'}

include_graphics("img/missingdayPeter.png")# from the playingaroundwiththicken.r file
# to do: make into 5 minute slots

>>>>

```{r, accuracyPlot,echo = FALSE,fig.cap="Measurement accuracy of each logged measurement. The x-axis denotes the accuracy in meters such that the user's actual location is expected to be within that radius with 67 percent confidence. Measures were classified into high accuracy (under 800m), medium accuracy (under 5000m) and low accuracy (over 5000m). Measures with accuracy of over 20000m were omitted from the graph. The maximum accuracy measure was over 40000m. Low accuracy measures are often near in time to more high accuracy measures.",out.width = '100%'}
#
include_graphics("img/journeyTillMiddayBoaz.png")

@@

```{r, measurementsPerDay,echo = FALSE,fig.cap="Missing data over time for the author. The x-axis denotes time, the y-axis shows how many measurements are made and each point is a day. The fill of the points shows the amount of hours of captured data each day.",out.width = '100%'}
#fix width
include_graphics("img/missingBoaz5minExample.png")# from the missingadataplot.R script
